---
title: "Supplementary Analaysis"
output: 
  rmarkdown::pdf_document:
    extra_dependencies: ["float"]
    fig_caption: yes 

header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options: 
  chunk_output_type: console

vignette: >
  %\VignetteIndexEntry{supplementary_materials}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

\beginsupplement
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,  echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
# Load packages
library(trolleyMultilabReplication)
library(tidyverse)
library(kableExtra)
library(gt)
library(countrycode)

# Read raw data
trolley_raw <- read_csv(system.file("extdata/trolley_raw.csv", package = "trolleyMultilabReplication"))

# Prepare datafiles for the analysis
# Save data for each study separately
study1a <- filter(trolley, include_study1a)
study1b <- filter(trolley, include_study1b)
study2a <- filter(trolley, include_study2a)
study2b <- filter(trolley, include_study2b)

# Save data but wihtouth the familiarity filter for each study
study1a_nf <- filter(trolley, include_study1a_withoutfamiliarity)
study1b_nf <- filter(trolley, include_study1b_withoutfamiliarity)
study2a_nf <- filter(trolley, include_study2a_withoutfamiliarity)
study2b_nf <- filter(trolley, include_study2b_withoutfamiliarity)

# Save data but with only those who failed the familiar exclusion criteria
study1a_f <- dplyr::filter(trolley, include_study1a_familiar)
study1b_f <- dplyr::filter(trolley, include_study1b_familiar)
study2a_f <- dplyr::filter(trolley, include_study2a_familiar)
study2b_f <- dplyr::filter(trolley, include_study2b_familiar)

# Add individualism and collectivism scales
study2a <- add_ind_col_scale(study2a)
study2b <- add_ind_col_scale(study2b)
study2a_nf <- add_ind_col_scale(study2a_nf)
study2b_nf <- add_ind_col_scale(study2b_nf)

# Add individualism and collectivism scales
trolley <- add_ind_col_scale(trolley)
```

```{r background information, echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
# Calculate background information
# Check if GBR001 is in the processed data
trolley %>% 
  distinct(survey_name, lab)

# Show the labs who are in the raw dataset but not in the processed
# Most likely these labs sent out the survey with the practice link
missing_labs <-
 trolley_raw %>%
 distinct(lab) %>%
 anti_join(., distinct(trolley_preprocessed, lab), by = "lab")

# Show the number of participants missing in each lab
trolley_raw %>%
 inner_join(., missing_labs, by = "lab") %>%
 count(lab) %>%
 ungroup() %>%
 mutate(all_n = sum(n))

# Show the number of participants excluded because of not finished responses
trolley_raw %>%
 dplyr::filter(str_detect(str_to_lower(practice), "false")) %>%
 dplyr::filter(!(lab == "TUR_021" & StartDate < lubridate::date("2020-04-22")),
        !(lab == "AUT_003" & StartDate < lubridate::date("2020-06-18")),
        !(lab == "USA_095")) %>%
 dplyr::filter(Progress < 98) %>%
 count()

# Show the number of labs
trolley %>% 
  distinct(lab) %>% 
  count()

trolley_raw %>% 
  distinct(lab) %>% 
  count()

# Number of responses
nrow(trolley)
nrow(trolley_raw)

# Number of languages
trolley_raw %>% 
  distinct(Q_Lang) %>% 
  drop_na(Q_Lang) %>% 
  count()
```

# 1. Demographics  

```{r dem2,echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
summaries <-
  trolley %>% 
  tidyr::nest(data = dplyr::everything()) %>% 
  dplyr::mutate(country_sum = purrr::map(data,
                            . %>% 
                             dplyr::group_by(Region, country3) %>% 
                             summarise_study() %>% 
                             left_join(cultural_distance, by = "country3") %>% 
                             add_column(grouping = "By country", .before = 1) %>% 
                             mutate(Country = countrycode::countrycode(sourcevar = country3, 
                                                          origin = "iso3c",
                                                          destination = "country.name")) %>% 
                             arrange(Region, Country)),
         region_sum = map(data, ~group_by(.x, Region) %>% 
                            summarise_study() %>% 
                            add_column(grouping = "By region", .before = 1) %>% 
                            arrange(Region)),
         all_sum =map(data, ~summarise_study(.x) %>% 
                        add_column(grouping = "All", .before = 1) %>% 
                        mutate(Region = "All")),
         # Add the 3 level summaries into one dateset
         bind_sum = pmap(list(country_sum, region_sum, all_sum), bind_rows))

demo_table <-
  summaries %>% 
  select(bind_sum) %>% 
  unnest(bind_sum) %>% 
  relocate(Country, .before = country3) %>% 
  select(-country3, -distance_year) %>% 
  gt(groupname_col = "grouping", 
     rowname_col = "Region") %>%
  fmt_number(columns = vars(`Age Mean`, `Age SD`),
             decimals = 1) %>% 
  cols_merge(columns = vars(`Age Mean`, `Age SD`), 
             pattern = "{1} ({2})") %>% 
  fmt_number(columns = vars(Collectivism),
             decimals = 3) %>% 
  fmt_percent(columns = vars(`Male %`, `Higher education %`),
              decimals = 1) %>% 
  fmt_missing(vars(Country, Collectivism, 
                   Region, grouping, `Higher education %`, 
                   `Male %`, `Age SD`)) %>% 
  gt::cols_label(`Age Mean` = "Age (SD)") %>% 
  gt::tab_footnote(footnote = "Distance from the US in collectivism. Some countries do not have a collectivism score.",
               locations = cells_column_labels(columns = vars(Collectivism))) %>% 
  gt::tab_options(row.striping.include_table_body = TRUE,
              row.striping.background_color = "#EEEEEE", 
              row.striping.include_stub = TRUE,
              row_group.background.color = "#999999", 
              column_labels.background.color = "#999999")

demo_table
```

# 2. Additional analysis
## Effect of physical contact and intention

In every cluster and for both types of dilemma we found good enough evidence supporting the alternative hypothesis when testing the effect of physical contact and the effect of intention. The summary of the results can be found in the tables below.

```{r physical contact , echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
# Comparing standard footbridge with footbridge pole in every cluster
additional_trolley <- 
  trolley %>% 
  filter(include_study1a | include_study2a) %>% 
  select(survey_name, survey_id, matches("trolley_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("trolley_1", "trolley_4") ~ "trolley_physical",
                                task %in% c("trolley_3", "trolley_2") ~ "trolley_intention",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

additional_speedboat <- 
  trolley %>% 
  filter(include_study1b | include_study2b) %>% 
  select(survey_name, survey_id, matches("speedboat_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("speedboat_1", "speedboat_4") ~ "speedboat_physical",
                                task %in% c("speedboat_3", "speedboat_2") ~ "speedboat_intention",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

bind_rows(additional_trolley, additional_speedboat) %>% 
  filter(str_detect(comparison, "intention|physical")) %>% 
  separate(comparison, into = c("Dilemma", "Comparison"), sep = "_") %>% 
  transmute(Cluster = str_remove(survey_name, "^[^_]*_"),
            Dilemma = str_to_title(Dilemma),
            Comparison = case_when(Comparison == "physical" ~ "Physical Contact",
                                   Comparison == "intention" ~ "Intention"),
            t,
            `Bf` = scales::scientific(bf),
            df,
            p = as.character(p),
            p = if_else(as.numeric(p) < .001, "< .001", p)) %>% 
  papaja::apa_table(
    caption = "Effect of Physical Contact and Intention",
    escape = TRUE)
```

```{r no familiarity, echo = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Additional analysis after all exclusions
# Comparing standard footbridge with footbridge pole in every cluster
additional_trolley <- 
  trolley %>% 
  filter(include_study1a_withoutfamiliarity | include_study2a_withoutfamiliarity) %>% 
  select(survey_name, survey_id, matches("trolley_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("trolley_1", "trolley_4") ~ "trolley_physical",
                                task %in% c("trolley_3", "trolley_2") ~ "trolley_intention",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

additional_speedboat <- 
  trolley %>% 
  filter(include_study1b_withoutfamiliarity | include_study2b_withoutfamiliarity) %>% 
  select(survey_name, survey_id, matches("speedboat_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("speedboat_1", "speedboat_4") ~ "speedboat_physical",
                                task %in% c("speedboat_3", "speedboat_2") ~ "speedboat_intention",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

bind_rows(additional_trolley, additional_speedboat) %>% 
  filter(str_detect(comparison, "intention|physical")) %>% 
  separate(comparison, into = c("Dilemma", "Comparison"), sep = "_") %>% 
  transmute(Cluster = str_remove(survey_name, "^[^_]*_"),
            Dilemma = str_to_title(Dilemma),
            Comparison = case_when(Comparison == "physical" ~ "Physical Contact",
                                   Comparison == "intention" ~ "Intention"),
            t,
            `Bf` = scales::scientific(bf),
            df,
            p = as.character(p),
            p = if_else(as.numeric(p) < .001, "< .001", p)) %>% 
  papaja::apa_table(
    caption = "Effect of Physical Contact and Intention",
    escape = TRUE,
    position= "h")
```

## Comparing the standard switch and standard footbridge dilemmas

When comparing the standard switch and standard footbridge dilemmas in all clusters for the trolley and the speedboat tasks we found good enough evidence in every case for the support of the alternative hypothesis. The summary results of each comparison separately can be found in Tables below.

```{r, standard switch and footbridge, echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
additional_trolley <- 
  trolley %>% 
  filter(include_study1a | include_study2a) %>% 
  select(survey_name, survey_id, matches("trolley_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("trolley_3", "trolley_4") ~ "trolley_standard",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

additional_speedboat <- 
  trolley %>% 
  filter(include_study1b | include_study2b) %>% 
  select(survey_name, survey_id, matches("speedboat_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("speedboat_3", "speedboat_4") ~ "speedboat_standard",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

bind_rows(additional_trolley, additional_speedboat) %>% 
  filter(str_detect(comparison, "standard")) %>% 
  separate(comparison, into = c("Dilemma", "Comparison"), sep = "_") %>% 
  transmute(Cluster = str_remove(survey_name, "^[^_]*_"),
            Dilemma = str_to_title(Dilemma),
            t,
            `Bf` = scales::scientific(bf),
            df,
            p = as.character(p),
            p = if_else(as.numeric(p) < .001, "< .001", p)) %>% 
  papaja::apa_table(
    caption = "Comparing the Standard Switch and Standard Footbridge Dilemmas",
    escape = TRUE,
    position="h")
```

```{r switch vs footbridge no familiarity, echo = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Additional analysis after all exclusions
additional_trolley <- 
  trolley %>% 
  filter(include_study1a_withoutfamiliarity | include_study2a_withoutfamiliarity) %>% 
  select(survey_name, survey_id, matches("trolley_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("trolley_3", "trolley_4") ~ "trolley_standard",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

additional_speedboat <- 
  trolley %>% 
  filter(include_study1b_withoutfamiliarity | include_study2b_withoutfamiliarity) %>% 
  select(survey_name, survey_id, matches("speedboat_[0-9]_rate")) %>% 
  pivot_longer(matches("_rate"), names_to = "task", names_pattern = "(.*)_rate", values_to = "rate") %>% 
  mutate(comparison = case_when(task %in% c("speedboat_3", "speedboat_4") ~ "speedboat_standard",
                                TRUE ~ NA_character_)) %>% 
  calculate_additional_table(.)

bind_rows(additional_trolley, additional_speedboat) %>% 
  filter(str_detect(comparison, "standard")) %>% 
  separate(comparison, into = c("Dilemma", "Comparison"), sep = "_") %>% 
  transmute(Cluster = str_remove(survey_name, "^[^_]*_"),
            Dilemma = str_to_title(Dilemma),
            t,
            `Bf` = scales::scientific(bf),
            df,
            p = as.character(p),
            p = if_else(as.numeric(p) < .001, "< .001", p)) %>% 
  papaja::apa_table(
    caption = "Comparing the Standard Switch and Standard Footbridge Dilemmas",
    escape = TRUE,
    position="h")
```

##Analysing familiar participants
As we registered, we conducted the analysis on familiar participants, the results can be found below.
```{r Study1ab Bayesian, echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
rscale <- .26
vars1a <- c("trolley_1_rate", "trolley_2_rate")
vars1b <- c("speedboat_1_rate", "speedboat_2_rate")

studys1a_results <- 
  bind_rows(calculate_study1_stat(study1a_f, vars = vars1a, 
                                  label = "Trolley", rscale = rscale),
            calculate_study1_stat(study1b_f, vars = vars1b, 
                                  label = "Speedboat", rscale = rscale)) %>% 
  # RR was calculated by manual iteration
  mutate(p = if_else(as.numeric(p) < .001, "<.001", p))

studys1a_results<-studys1a_results[, -4]

kbl(
  studys1a_results,
  col.names = c("Dilemma", "Cluster", "BF", "t", "df", "p", "Cohen's d"),
  format = "latex",
  booktabs = T,
  escape = T,
  caption = "The effect of personal force on moral dilemma judgements (familiar particiapnts)",
  centering = T,
  position = "H") %>%
  kable_styling(full_width = F,  position = "left") %>%
  row_spec(row = 0, bold = TRUE) %>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")
```

```{r Study2ab Bayesian, echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE}
rscaleFixed <- c("personal_force:intention" = 0.19)
vars2a <- c("trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate")
vars2b <- c("speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate")

studys2a_results <- 
  bind_rows(calculate_study2_stat(study2a_f, vars = vars2a, 
                                  label = "Trolley", rscaleFixed = rscaleFixed), 
            calculate_study2_stat(study2b_f, vars = vars2b, 
                                  label = "Speedboat", rscaleFixed = rscaleFixed)) %>% 
  # RR was calculated by manual iteration
  mutate( p = if_else(as.numeric(p) < .001, "<.001", p))

studys2a_results<-studys2a_results[, -(4)]

kbl(
  studys2a_results,
  col.names = c("Dilemma", "Cluster", "BF", "F", "df", "p", 'Partial $\\eta^2$', "Raw effect"),
  format = "latex",
  booktabs = T,
  escape = F,
  caption = "The interaction of personal force and intention on moral dilemma judgemnts (familiar participants)",
  centering = T,
  position = "H") %>%
  kable_styling(full_width = F,  position = "left", latex_options = "scale_down") %>%
  row_spec(row = 0, bold = TRUE) %>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major", row_group_label_position = "identity")
```


## Oxford utilitarianism Scale

As we registered, we simply publish descriptive statistics of the Oxford Utilitarianism Scale in each cultural clusters.We applied no exclusion criteria during this analysis.

```{r, fig.pos = "H" ,out.width = "80%", fig.cap = "Results on the Oxford Utilitarianism Scale",echo = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE }
# Prepare data for plotting
plot_data <-
  trolley %>%
  filter(include_noproblem) %>% 
  select(survey_name, lab, ResponseId, contains("oxford_")) %>%
  pivot_longer(
    contains("oxford_"),
    names_to = "item_no",
    values_to = "rate",
    names_prefix = "oxford_utilitarian_") %>%
  mutate(item_no = as.integer(item_no),
         subscale = case_when(item_no == 1L ~ "Impartial Beneficence",
                              item_no == 2L ~ "Instrumental Harm",
                              item_no == 3L ~ "Impartial Beneficence",
                              item_no == 4L ~ "Instrumental Harm",
                              item_no == 5L ~ "Impartial Beneficence",
                              item_no == 6L ~ "Instrumental Harm",
                              item_no == 7L ~ "Impartial Beneficence",
                              item_no == 8L ~ "Instrumental Harm",
                              item_no == 9L ~ "Impartial Beneficence",
                              TRUE ~ NA_character_),
         survey_name = str_remove(survey_name, "PSA006_")) %>% 
  drop_na(rate)

# Create plot
plot_data %>% 
  ggplot() +
  aes(
    x = subscale,
    y = rate,
    width = 0.7) +
  geom_boxplot() +
  facet_wrap(facets = vars(survey_name)) +
  labs(
    y = "Rating",
    x = "Subscale") +
  scale_y_continuous(
    breaks = 1:7,
    labels = as.character(1:7)) + 
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(hjust = 0.5, vjust = 0.5, face = "bold", size = 17),
    axis.title.x = element_blank(),
    axis.title.y = element_text(face = "bold", size = 10),
    axis.text.x = element_text(face = "bold", size = 7, colour = "Black"),
    axis.text.y = element_text(face = "bold", size = 12, colour = "Black"),
    legend.title = element_blank(),
    legend.text = element_text(size = 9))
```


#Exploratory analysis on overall utilitarianism and collectivism

Although not part of the planned analysis, we hypothesized that country-level collectivism would be negatively associated with utilitarian responding (i.e., higher morall acceptibility ratings). We found no evidence for this hypothesis, regardless of familiarity exclusion or dilemma context. Interestingly, however, we found strong evidence for the association between vertical individualism and average moral acceptibility ratings on moral dilemmas, regardless of dilemma context or exclusion criteria. The positive association means that higher levels of vertical individualism is associated with higher acceptance of the utilitarian response option. Although we hypothesized that it would be collectivism that makes people *more* emotional and therefore, less utilitarian, we speculate that individualism made people *less* emotional and therefore, more utilitarian.

In all of the regression models below, we added the random intercept of countries.


```{r analysis individual + country level study 2a, echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}

utilitarian_trolley <- filter(trolley, include_study1a|include_study2a)
utilitarian_trolley_nf <- filter(trolley, include_study1a_withoutfamiliarity|include_study2a_withoutfamiliarity)

tabledata_sa_ind <-  
  utilitarian_trolley %>% 
  left_join(., cultural_distance, by = "country3") %>% 
  calculate_culture_utilitarianism(study_type="trolley")

tabledata_sa_ind_tidy <-tidy_culture_utilitarianism(tabledata_s2a_ind)

tabledata_sa_ind_f <-  
  utilitarian_trolley_nf %>% 
  left_join(., cultural_distance, by = "country3") %>% 
  calculate_culture_utilitarianism(study_type="trolley")

tabledata_sa_ind_f_tidy <- tidy_culture_utilitarianism(tabledata_sa_ind_f)

full_table_trolley=merge(tabledata_sa_ind_tidy, tabledata_sa_ind_f_tidy, by="variable")
full_table_trolley=full_table_trolley[, -c(4,5,9,10)]

kbl(
  full_table_trolley,
  format = "latex",
  col.names = c("Variable", "BF", "b", "p", "BF", "b", "p"),
  booktabs = TRUE,
  escape = TRUE,
  caption = "Is the interaction of personal force and intention affected by individualism/collectivism on Trolley dilemmas?",
  centering = TRUE,
  position = "H") %>%
  kable_styling(full_width = FALSE,  position = "left") %>%
  row_spec(row = 0, bold = TRUE) %>%
  add_header_above(c(" " = 1, "With familiarity exclusion" = 3, "No familiarity exclusion" = 3))

```

```{r analysis individual + country level study 2b, echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}

utilitarian_speedboat <- filter(trolley, include_study1b|include_study2b)
utilitarian_speedboat_nf <- filter(trolley, include_study1b_withoutfamiliarity|include_study2b_withoutfamiliarity)

tabledata_sb_ind <-  
  utilitarian_speedboat %>% 
  left_join(., cultural_distance, by = "country3") %>% 
  calculate_culture_utilitarianism(study_type="speedboat")

tabledata_sb_ind_tidy <-tidy_culture_utilitarianism(tabledata_sb_ind)

tabledata_sb_ind_f <-  
  utilitarian_speedboat_nf %>% 
  left_join(., cultural_distance, by = "country3") %>% 
  calculate_culture_utilitarianism(study_type="speedboat")

tabledata_sb_ind_f_tidy <- tidy_culture_utilitarianism(tabledata_sb_ind_f)

full_table_trolley=merge(tabledata_sb_ind_tidy, tabledata_sb_ind_f_tidy, by="variable")
full_table_trolley=full_table_trolley[, -c(4,5,9,10)]

kbl(
  full_table_trolley,
  format = "latex",
  col.names = c("Variable", "BF", "b", "p", "BF", "b", "p"),
  booktabs = TRUE,
  escape = TRUE,
  caption = "Is the interaction of personal force and intention affected by individualism/collectivism on Speedboat dilemmas?",
  centering = TRUE,
  position = "H") %>%
  kable_styling(full_width = FALSE,  position = "left") %>%
  row_spec(row = 0, bold = TRUE) %>%
  add_header_above(c(" " = 1, "With familiarity exclusion" = 3, "No familiarity exclusion" = 3))

```

##With all exclusions

```{r study2a overall individualism plot, fig.pos="H",out.width="80%",fig.cap="Correlation between country-level individualism/collectivism and moral accessibility ratings on the Trolley dilemmas (higher moral acceptibility means higher acceptibility of the utilitarian choice).", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
plot_data_country <- prepare_plot_data_country_means(utilitarian_trolley, "trolley")

```

```{r study2a vertical horizontal individualism, out.width="80%", fig.cap="Personal level individualism/collectivism effects on moral acceptibility ratings (trolley dilemmas)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}

graphdata <- 
  tabledata_sa_ind_tidy %>% 
  filter(variable != "Country-level collectivism") %>% 
  select(variable, b, lower, higher)

create_plot_ind_col(graphdata)


```

```{r study2b overall individualism plot, fig.pos="H",out.width="80%",fig.cap="Correlation between country-level individualism/collectivism and moral accessibility ratings on the Speedboat dilemmas (higher moral acceptibility means higher acceptibility of the utilitarian choice)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
##cohen d calculation for every country
#scatterplot: x effect size, y individualism
#size of dots: cohen d
countrydata=data.frame(country=levels(factor(utilitarian_speedboat$country3)), matrix(nrow=length(levels(factor(utilitarian_speedboat$country3))),ncol=3, dimnames=list(levels(factor(utilitarian_speedboat$country3)), c("cohend","Collectivism","N") )))

for (i in levels(factor(utilitarian_speedboat$country3))){
  d=subset(utilitarian_speedboat, country3==i, select=c("speedboat_1_rate", "speedboat_2_rate", "speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"))
  dat_long=na.omit(melt(data=d, variable.name = "condition", value.name="rate"))
  if (length(dat_long$rate)<10){
    countrydata[i,"cohend"]=NA
  }else{
    countrydata[i,"cohend"]=mean(dat_long$rate)
  }
  countrydata[i,"Collectivism"]=mean(utilitarian_speedboat[utilitarian_speedboat$country3==i,]$Collectivism, na.rm=T)
  countrydata[i,"N"]=length(dat_long$rate)
}

countrydata=na.omit(countrydata)
ggplot(countrydata, aes(x=cohend, y=Collectivism, label=country)) +
  geom_point(aes(size=N))+
  geom_text(hjust=-0.2,size=3)+
geom_smooth(method = "lm", mapping = aes(weight = N), color = "blue", show.legend = FALSE, se=F)+xlab("Average moral acceptibility rating")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_text(face="bold", size=12, colour="Black"), axis.title.y=element_text(face="bold", size=12, colour="Black"), axis.text.x = element_text(face="bold", size=10, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_text(face="bold", size=10, colour="Black"),legend.text=element_text(size=9))
  
  

```

```{r study2b vertical horizontal individualism,  out.width="80%", fig.cap="Personal level individualism/collectivism effects on moral acceptibility ratings (speedboat dilemmas)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}


graphdata <- 
  tabledata_sb_ind_tidy %>% 
  filter(variable != "Country-level collectivism") %>% 
  select(variable, b, lower, higher)

create_plot_ind_col(graphdata)



```


##Without familiarity exclusion

```{r study2a overall individualism plot w/o exc, fig.pos="H",out.width="80%",fig.cap="Correlation between country-level individualism/collectivism and moral accessibility ratings on the Trolley dilemmas (higher moral acceptibility means higher acceptibility of the utilitarian choice)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
##cohen d calculation for every country
#scatterplot: x effect size, y individualism
#size of dots: cohen d
countrydata=data.frame(country=levels(factor(utilitarian_trolley$country3)), matrix(nrow=length(levels(factor(utilitarian_trolley$country3))),ncol=3, dimnames=list(levels(factor(utilitarian_trolley$country3)), c("cohend","Collectivism","N") )))

for (i in levels(factor(utilitarian_trolley$country3))){
  d=subset(utilitarian_trolley, country3==i, select=c("trolley_1_rate", "trolley_2_rate", "trolley_3_rate", "trolley_4_rate", "trolley_5_rate", "trolley_6_rate"))
  dat_long=na.omit(melt(data=d, variable.name = "condition", value.name="rate"))
  if (length(dat_long$rate)<10){
    countrydata[i,"cohend"]=NA
  }else{
    countrydata[i,"cohend"]=mean(dat_long$rate)
  }
  countrydata[i,"Collectivism"]=mean(utilitarian_trolley[utilitarian_trolley$country3==i,]$Collectivism, na.rm=T)
  countrydata[i,"N"]=length(dat_long$rate)
}

countrydata=na.omit(countrydata)
ggplot(countrydata, aes(x=cohend, y=Collectivism, label=country)) +
  geom_point(aes(size=N))+
  geom_text(hjust=-0.2,size=3)+
geom_smooth(method = "lm", mapping = aes(weight = N), color = "blue", show.legend = FALSE, se=F)+xlab("Average moral acceptibility rating")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_text(face="bold", size=12, colour="Black"), axis.title.y=element_text(face="bold", size=12, colour="Black"), axis.text.x = element_text(face="bold", size=10, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_text(face="bold", size=10, colour="Black"),legend.text=element_text(size=9))
  
  

```


```{r study2a vertical horizontal individualism w/o excl, out.width="80%", fig.cap="Personal level individualism/collectivism effects on moral acceptibility ratings (trolley dilemmas)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}


graphdata <- 
  tabledata_sa_ind_f_tidy %>% 
  filter(variable != "Country-level collectivism") %>% 
  select(variable, b, lower, higher)

create_plot_ind_col(graphdata)


```


```{r study2b overall individualism plot w/o excl, fig.pos="H",out.width="80%",fig.cap="Correlation between country-level individualism/collectivism and moral accessibility ratings on the Speedboat dilemmas (higher moral acceptibility means higher acceptibility of the utilitarian choice)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
##cohen d calculation for every country
#scatterplot: x effect size, y individualism
#size of dots: cohen d
countrydata=data.frame(country=levels(factor(utilitarian_speedboat$country3)), matrix(nrow=length(levels(factor(utilitarian_speedboat$country3))),ncol=3, dimnames=list(levels(factor(utilitarian_speedboat$country3)), c("cohend","Collectivism","N") )))

for (i in levels(factor(utilitarian_speedboat$country3))){
  d=subset(utilitarian_speedboat, country3==i, select=c("speedboat_1_rate", "speedboat_2_rate", "speedboat_3_rate", "speedboat_4_rate", "speedboat_5_rate", "speedboat_6_rate"))
  dat_long=na.omit(melt(data=d, variable.name = "condition", value.name="rate"))
  if (length(dat_long$rate)<10){
    countrydata[i,"cohend"]=NA
  }else{
    countrydata[i,"cohend"]=mean(dat_long$rate)
  }
  countrydata[i,"Collectivism"]=mean(utilitarian_speedboat[utilitarian_speedboat$country3==i,]$Collectivism, na.rm=T)
  countrydata[i,"N"]=length(dat_long$rate)
}

countrydata=na.omit(countrydata)
ggplot(countrydata, aes(x=cohend, y=Collectivism, label=country)) +
  geom_point(aes(size=N))+
  geom_text(hjust=-0.2,size=3)+
geom_smooth(method = "lm", mapping = aes(weight = N), color = "blue", show.legend = FALSE, se=F)+xlab("Average moral acceptibility rating")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),plot.title=element_text( hjust=0.5, vjust=0.5, face="bold", size=17),
        axis.title.x=element_text(face="bold", size=12, colour="Black"), axis.title.y=element_text(face="bold", size=12, colour="Black"), axis.text.x = element_text(face="bold", size=10, colour="Black"), axis.text.y = element_text(face="bold", size=12, colour="Black"),
        legend.title=element_text(face="bold", size=10, colour="Black"),legend.text=element_text(size=9))
  


```


```{r study2b vertical horizontal individualism w/o excl,  out.width="80%", fig.cap="Personal level individualism/collectivism effects on moral acceptibility ratings (speedboat dilemmas)", echo =FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}


graphdata <- 
  tabledata_sb_ind_f_tidy %>% 
  filter(variable != "Country-level collectivism") %>% 
  select(variable, b, lower, higher)

create_plot_ind_col(graphdata)



```
